Bayesian Inference Using Sequential Monte-Carlo Algorithm for Dynamic System Models

### 2020-08-05 MSc-dissertation.tex
New para

@@

\begin{table}[h!]
\centering
\begin{tabular}{|c c c|} 
 \hline
 Parameter & Definition & Units\\ [0.5ex] 
 \hline\hline
 $\lambda_N$ & Self-increase rate of neutrophil & $cell/h$  \\ 
 $\kappa_{N\beta}$ & Promoting effect coefficient by il-1$\beta$ & $cell/(unit\cdotp h)$\\
 $\mu_N$ & Coefficient of negative feedback of $N$ & $h^{-1}$ \\
 $\nu_{N\Phi}$ & Coefficient of inhibition of both $N$ and $\Phi$& $cell^{-1}\cdotp h^{-1}$ \\
 \hline
 $\lambda_\Phi$ & Self-increase rate of macrophage & $cell/h$ \\
 $\kappa_{\Phi\beta}$ & Promoting effect coefficient by il-1$\beta$ & $cell/(unit\cdotp h)$ \\
 $\mu_\Phi$ &  Coefficient of negative feedback of $\Phi$ & $h^{-1}$ \\
 \hline
 $s_{\beta N}$ & Production rate from $N$ & $unit/(cell\cdotp h)$ \\
 $i_{\beta\Phi}$ & Coefficient of inhibition to the production & $cell^{-1}$ \\
 $\mu_\beta$ & Coefficient of negative feedback of $\beta$ & $h^{-1}$ \\
 \hline
 $s_{\alpha\Phi}$ & Production rate from $\Phi$ & $unit/(cell\cdotp h)$ \\
 $\mu_\alpha$ & Coefficient of negative feedback of $\alpha$ & $h^{-1}$ \\
 \hline
\end{tabular}
\caption{Parameters introduced in the basic model (model 1) [REMOVE unit]}
\label{table:m1}
\end{table}

@@

\begin{table}[h!]
    \centering
    \begin{tabular}{|c c c|} 
     \hline
     Parameter & Definition & Units\\ [0.5ex] 
     \hline\hline
     $d_{\beta\alpha}$ & Coefficient of promoting effect from $\beta$ & $h^{-1}$  \\ 
     \hline
     $f_{\beta\alpha}$ & Coefficient of promoting the production of $\alpha$ by $\beta$ & $cell^{-1}\cdotp h^{-1}$  \\ 
     \hline
    \end{tabular}
    \caption{Parameters introduced in model 4 and 5}
    \label{table:m45}
\end{table}

@@

\begin{table}[t!]
    \centering
    \begin{tabular}{|c c c|} 
     \hline
     Parameter & Estimated mean  & Estimated mean  \\ 
      & value (uniform) &value (log-uniform) \\[0.5ex] 
     \hline\hline
     $\lambda_N$ & 14.1 & 13.3 \\ 
     $a$ & 9.67 & 0.0170  \\ 
     $\kappa_{N\beta}$ & 18.0 & 0.259 \\
     $\mu_N$ & 13.2 & 0.0180 \\
     $\nu_{N\Phi}$ & 0.742 & 0.131 \\
     \hline
     $\kappa_{\Phi\beta}$ & 0.239 & 0.156 \\
     $\mu_\Phi$ & 0.154 & 0.0350 \\
     \hline
     $s_{\beta N}$ & 6.75 & 1.21 \\
     $\mu_\beta$ & 6.38 & 1.32 \\
     \hline
     $s_{\alpha\Phi}$ & 17.0 & 5.83 \\
     $\mu_\alpha$ & 11.9 & 2.43\\
     \hline
    \end{tabular}
    \caption[Estimated parameter values of model 3]
    {Estimated parameter values of model 3, using uniform prior distribution and log-uniform prior distribution respectively}
    \label{table:estimated1}
\end{table}

@@

\begin{table}[h!]
    \centering
    \begin{tabular}{|c c|} 
     \hline
     Environment & Version \\ [0.5ex] 
     \hline\hline
     $\lambda_N$ & 2.1989  \\ 
     $\kappa_{N\beta}$ & 3.9627  \\
     $\mu_N$ & 1.7219 \\
     $\nu_{N\Phi}$  0.2195 & $cell^{-1}\cdotp h^{-1}$ \\
     \hline
     $\lambda_\Phi$ & 1.3146  $cell/h$ \\
     $\kappa_{\Phi\beta}$ 0.1235 & $cell/(unit\cdotp h)$ \\
     $\mu_\Phi$  0.1454 & $h^{-1}$ \\
     \hline
     $s_{\beta N}$ &6.5536  $unit/(cell\cdotp h)$ \\
     $i_{\beta\Phi}$  1.7062 & $cell^{-1}$ \\
     $\mu_\beta$ &0.5212  $h^{-1}$ \\
     \hline
     $s_{\alpha\Phi}$  10.2416 & $unit/(cell\cdotp h)$ \\
     $\mu_\alpha$ 19.6642 & $h^{-1}$ \\
    [1ex] 
     \hline
    \end{tabular}
    \caption{Environment on local machine}
    \label{table:local_macine}
\end{table}

@@

\begin{table}[h!]
    \centering
    \begin{tabular}{|c c|} 
     \hline
     Environment & Version \\ [0.5ex] 
     \hline\hline
     $\lambda_N$ & 2.1989  \\ 
     $\kappa_{N\beta}$ & 3.9627  \\
     $\mu_N$ & 1.7219 \\
     $\nu_{N\Phi}$  0.2195 & $cell^{-1}\cdotp h^{-1}$ \\
     \hline
     $\lambda_\Phi$ & 1.3146  $cell/h$ \\
     $\kappa_{\Phi\beta}$ 0.1235 & $cell/(unit\cdotp h)$ \\
     $\mu_\Phi$  0.1454 & $h^{-1}$ \\
     \hline
     $s_{\beta N}$ &6.5536  $unit/(cell\cdotp h)$ \\
     $i_{\beta\Phi}$  1.7062 & $cell^{-1}$ \\
     $\mu_\beta$ &0.5212  $h^{-1}$ \\
     \hline
     $s_{\alpha\Phi}$  10.2416 & $unit/(cell\cdotp h)$ \\
     $\mu_\alpha$ 19.6642 & $h^{-1}$ \\
    [1ex] 
     \hline
    \end{tabular}
    \caption{Environment on remote machine}
    \label{table:remote_macine}
\end{table}

@@

\begin{table}[h!]
    \centering
    \begin{tabular}{|c c c|} 
     \hline
     Parameter & Value & Unit\\ [0.5ex] 
     \hline\hline
     $\lambda_N$ & 2.20 & $cell/h$  \\ 
     $\kappa_{N\beta}$ & 3.96 & $cell/(unit\cdotp h)$\\
     $\mu_N$ & 1.72 & $h^{-1}$\\
     $\nu_{N\Phi}$ & 0.220 & $cell^{-1}\cdotp h^{-1}$ \\
     \hline
     $\lambda_\Phi$ & 1.31 & $cell/h$ \\
     $\kappa_{\Phi\beta}$ & 0.124 & $cell/(unit\cdotp h)$ \\
     $\mu_\Phi$ & 0.145 & $h^{-1}$ \\
     \hline
     $s_{\beta N}$ & 6.554 & $unit/(cell\cdotp h)$ \\
     $i_{\beta\Phi}$ & 1.71 & $cell^{-1}$ \\
     $\mu_\beta$ & 0.521 & $h^{-1}$ \\
     \hline
     $s_{\alpha\Phi}$ & 10.2 & $unit/(cell\cdotp h)$ \\
     $\mu_\alpha$ & 19.1 & $h^{-1}$ \\
     \hline
    \end{tabular}
    \caption{Parameter values used for model 1}
    \label{table:m1}
\end{table}

@@

>>>>

Compared to mammals, zebrafish can regenerate spinal cord after injury, and possibly recover swimming function. They are widely used in regenerative ability researches. Experiments found that although being cut off, the axonal of nerve cells can regenerate and bridge across the lesion site, which critically determined whether zebrafish can regain the swimming function \cite{axonal}. Tsarouchas et al. \cite{ref:Tsarouchas} studied the the complex interactions happen at the lesion site. The inflammation affects the regeneration, as if it is promoted, it accelerates the axonal regeneration; if it is inhibited, it reduces the regeneration. Further experiments showed that two kinds of cytokines, il-1$\beta$ and tnf-$\alpha$, affect the inflammation, which are dynamically controlled by immunes cells, i.e. cytokines works as media to control the regeneration. Here cytokines are small proteins, work as messenger to pass signal across different cells, which are similar to hormones and neurotransmitter.

An interaction map can be drawn, according to the evidences found in \cite{ref:Tsarouchas}. After injury, a massive immune response was observed, with the increasing numbers of several kinds of cells: macrophage, neutrophil and keratinocyte. The dynamical system consists of complex interactions between cells and cytokines, e.g. the increasing tnf-$\alpha$

@@

\begin{table}[h!]
    \centering
    \begin{tabular}{|c c c|}
        \hline
        Parameter            & Definition                                       & Units                    \\ [0.5ex]
        \hline\hline
        $\lambda_N$          & Self-increase rate of neutrophil                 & $cell/h$                 \\
        $\kappa_{N\beta}$    & Promoting effect coefficient by il-1$\beta$      & $cell/(unit\cdotp h)$    \\
        $\mu_N$              & Coefficient of negative feedback of $N$          & $h^{-1}$                 \\
        $\nu_{N\Phi}$        & Coefficient of inhibition of both $N$ and $\Phi$ & $cell^{-1}\cdotp h^{-1}$ \\
        \hline
        $\lambda_\Phi$       & Self-increase rate of macrophage                 & $cell/h$                 \\
        $\kappa_{\Phi\beta}$ & Promoting effect coefficient by il-1$\beta$      & $cell/(unit\cdotp h)$    \\
        $\mu_\Phi$           & Coefficient of negative feedback of $\Phi$       & $h^{-1}$                 \\
        \hline
        $s_{\beta N}$        & Production rate from $N$                         & $unit/(cell\cdotp h)$    \\
        $i_{\beta\Phi}$      & Coefficient of inhibition to the production      & $cell^{-1}$              \\
        $\mu_\beta$          & Coefficient of negative feedback of $\beta$      & $h^{-1}$                 \\
        \hline
        $s_{\alpha\Phi}$     & Production rate from $\Phi$                      & $unit/(cell\cdotp h)$    \\
        $\mu_\alpha$         & Coefficient of negative feedback of $\alpha$     & $h^{-1}$                 \\
        \hline
    \end{tabular}
    \caption{Parameters introduced in the basic model (model 1) [REMOVE unit]}
    \label{table:m1}
\end{table}

@@

\begin{table}[h!]
    \centering
    \begin{tabular}{|c c c|}
        \hline
        Parameter         & Definition                                                     & Units                    \\ [0.5ex]
        \hline\hline
        $d_{\beta\alpha}$ & Coefficient of promoting effect from $\beta$                   & $h^{-1}$                 \\
        \hline
        $f_{\beta\alpha}$ & Coefficient of promoting the production of $\alpha$ by $\beta$ & $cell^{-1}\cdotp h^{-1}$ \\
        \hline
    \end{tabular}
    \caption{Parameters introduced in model 4 and 5}
    \label{table:m45}
\end{table}

@@

\begin{table}[t!]
    \centering
    \begin{tabular}{|c c c|}
        \hline
        Parameter            & Estimated mean  & Estimated mean      \\
                             & value (uniform) & value (log-uniform) \\[0.5ex]
        \hline\hline
        $\lambda_N$          & 14.1            & 13.3                \\
        $a$                  & 9.67            & 0.0170              \\
        $\kappa_{N\beta}$    & 18.0            & 0.259               \\
        $\mu_N$              & 13.2            & 0.0180              \\
        $\nu_{N\Phi}$        & 0.742           & 0.131               \\
        \hline
        $\kappa_{\Phi\beta}$ & 0.239           & 0.156               \\
        $\mu_\Phi$           & 0.154           & 0.0350              \\
        \hline
        $s_{\beta N}$        & 6.75            & 1.21                \\
        $\mu_\beta$          & 6.38            & 1.32                \\
        \hline
        $s_{\alpha\Phi}$     & 17.0            & 5.83                \\
        $\mu_\alpha$         & 11.9            & 2.43                \\
        \hline
    \end{tabular}
    \caption[Estimated parameter values of model 3]
    {Estimated parameter values of model 3, using uniform prior distribution and log-uniform prior distribution respectively}
    \label{table:estimated1}
\end{table}

@@

\begin{table}[h!]
    \centering
    \begin{tabular}{|c c|}
        \hline
        Environment                 & Version                       \\ [0.5ex]
        \hline\hline
        $\lambda_N$                 & 2.1989                        \\
        $\kappa_{N\beta}$           & 3.9627                        \\
        $\mu_N$                     & 1.7219                        \\
        $\nu_{N\Phi}$  0.2195       & $cell^{-1}\cdotp h^{-1}$      \\
        \hline
        $\lambda_\Phi$              & 1.3146  $cell/h$              \\
        $\kappa_{\Phi\beta}$ 0.1235 & $cell/(unit\cdotp h)$         \\
        $\mu_\Phi$  0.1454          & $h^{-1}$                      \\
        \hline
        $s_{\beta N}$               & 6.5536  $unit/(cell\cdotp h)$ \\
        $i_{\beta\Phi}$  1.7062     & $cell^{-1}$                   \\
        $\mu_\beta$                 & 0.5212  $h^{-1}$              \\
        \hline
        $s_{\alpha\Phi}$  10.2416   & $unit/(cell\cdotp h)$         \\
        $\mu_\alpha$ 19.6642        & $h^{-1}$                      \\
        [1ex]
        \hline
    \end{tabular}
    \caption{Environment on local machine}
    \label{table:local_macine}
\end{table}

@@

\begin{table}[h!]
    \centering
    \begin{tabular}{|c c|}
        \hline
        Environment                 & Version                       \\ [0.5ex]
        \hline\hline
        $\lambda_N$                 & 2.1989                        \\
        $\kappa_{N\beta}$           & 3.9627                        \\
        $\mu_N$                     & 1.7219                        \\
        $\nu_{N\Phi}$  0.2195       & $cell^{-1}\cdotp h^{-1}$      \\
        \hline
        $\lambda_\Phi$              & 1.3146  $cell/h$              \\
        $\kappa_{\Phi\beta}$ 0.1235 & $cell/(unit\cdotp h)$         \\
        $\mu_\Phi$  0.1454          & $h^{-1}$                      \\
        \hline
        $s_{\beta N}$               & 6.5536  $unit/(cell\cdotp h)$ \\
        $i_{\beta\Phi}$  1.7062     & $cell^{-1}$                   \\
        $\mu_\beta$                 & 0.5212  $h^{-1}$              \\
        \hline
        $s_{\alpha\Phi}$  10.2416   & $unit/(cell\cdotp h)$         \\
        $\mu_\alpha$ 19.6642        & $h^{-1}$                      \\
        [1ex]
        \hline
    \end{tabular}
    \caption{Environment on remote machine}
    \label{table:remote_macine}
\end{table}

@@

\begin{table}[h!]
    \centering
    \begin{tabular}{|c c c|}
        \hline
        Parameter            & Value & Unit                     \\ [0.5ex]
        \hline\hline
        $\lambda_N$          & 2.20  & $cell/h$                 \\
        $\kappa_{N\beta}$    & 3.96  & $cell/(unit\cdotp h)$    \\
        $\mu_N$              & 1.72  & $h^{-1}$                 \\
        $\nu_{N\Phi}$        & 0.220 & $cell^{-1}\cdotp h^{-1}$ \\
        \hline
        $\lambda_\Phi$       & 1.31  & $cell/h$                 \\
        $\kappa_{\Phi\beta}$ & 0.124 & $cell/(unit\cdotp h)$    \\
        $\mu_\Phi$           & 0.145 & $h^{-1}$                 \\
        \hline
        $s_{\beta N}$        & 6.554 & $unit/(cell\cdotp h)$    \\
        $i_{\beta\Phi}$      & 1.71  & $cell^{-1}$              \\
        $\mu_\beta$          & 0.521 & $h^{-1}$                 \\
        \hline
        $s_{\alpha\Phi}$     & 10.2  & $unit/(cell\cdotp h)$    \\
        $\mu_\alpha$         & 19.1  & $h^{-1}$                 \\
        \hline
    \end{tabular}
    \caption{Parameter values used for model 1}
    \label{table:m1}
\end{table}

@@

    \bibitem{axonal} Becker, T., Wullimann, M.F., Becker, C.G., Bernhardt, R.R. and Schachner, M., 1997. Axonal regrowth after spinal cord transection in adult zebrafish. Journal of Comparative Neurology, 377(4), pp.577-595.
